\begin{thebibliography}{}

\bibitem{cite1}
Botte, M., Pariota, L., D’Acierno, L., & Bifulco, G. (2019). An Overview of Cooperative Driving in the European Union: Policies and Practices. Electronics, 8(6), 616. https://doi.org/10.3390/electronics8060616

\bibitem{cite2}
Manesis, S. (2001). HARD PLATOONING VERSUS SOFT PLATOONING IN LARGE-SCALE HIGHWAY TRANSPORTATION SYSTEMS. University Ojpatras.

\bibitem{cite3}
van Willigen, W., Schut, M., & Kester, L. Approximating Safe Spacing Policies for Adaptive Cruise Control Strategies.

\bibitem{cite4}
Hallé, S. (2005). AUTOMATED HIGHWAY SYSTEMS: PLATOONS OF VEHICLES VIEWED AS A MULTIAGENT SYSTEM (M.Sc.). FACULTÉ DES SCIENCES ET DE GÉNIE UNIVERSITÉ LAVAL QUÉBEC.

\bibitem{cite5}
Ajaykumar, & Krishna, L. (2016). Automated Lane Changing using Automated Vehicles with Disruption Minimization. International Journal Of Advanced Research In Computer And Communication Engineering, Vol. 5(Issue 6). Retrieved 23 April 2021, from.

\bibitem{cite6}
Shladover, S. (2005). Automated vehicles for highway operations (automated highway systems). Proceedings Of The Institution Of Mechanical Engineers, Part I: Journal Of Systems And Control Engineering, 219(1), 53-75. https://doi.org/10.1243/095440705x9407

\bibitem{cite7}
Eilers, S., Martensson, J., Pettersson, H., Pillado, M., Gallegos, D., & Tobar, M. et al. (2015). COMPANION -- Towards Co-operative Platoon Management of Heavy-Duty Vehicles. 2015 IEEE 18Th International Conference On Intelligent Transportation Systems. https://doi.org/10.1109/itsc.2015.208

\bibitem{cite8}
WANG, L., SYED, A., YIN, G., PANDYA, A., & ZHANG, H. (2013). Control of Vehicle Platoons for Highway Safety and Efficient Utility: Consensus with Communications and Vehicle Dynamics. J Syst Sci Complex. Retrieved 23 April 2021, from.

\bibitem{cite9}
Chan, E., Gilhead, P., Jelínek, P., Krejčí, P., & Robinson, T. (2012). Robinson. ITS World Congress. Retrieved 23 April 2021, from.

\bibitem{cite10}
Dao, T., Michael Clark, C., & Huissoon, J. Distributed Platoon Assignment and Lane Selection for Traffic Flow Optimization. Retrieved 23 April 2021, from.

\bibitem{cite12}
Caruntu, C., Maxim, A., & Rafaila, R. (2018). Multiple-Lane Vehicle Platooning based on a Multi-Agent Distributed Model Predictive Control Strategy*. 22Nd International Conference On System Theory, (22). Retrieved 23 April 2021, from.

\bibitem{citeE1}
EL-Zaher, M., Dafflon, B., Gechter, F., & Contet, J. (2012). Vehicle Platoon Control with Multi-configuration Ability. Procedia Computer Science, 9, 1503-1512. https://doi.org/10.1016/j.procs.2012.04.165

\bibitem{citeE2}
P. HOOGENDOORN, S. (2001). Platoon-Based Multiclass Modeling of Multilane Trafic Flow. Kluwer Academic Publishers. Retrieved 23 April 2021, from.

\bibitem{citeE3}
ELENA KALBITZ, T. (2017). A COMPARISON OF APPROACHES FOR PLATOONING MANAGEMENT (M. Sc.). Universität Mannheim.

\bibitem{citeE4}
Dao, T., Michael Clark, C., & Huissoon, J. (2007). Optimized Lane Assignment Using Inter-Vehicle Communication. IEEE Intelligent Vehicles Symposium. Retrieved 23 April 2021, from.

\end{thebibliography}